### 2018-12-10 reports/thesis/chapters/5_inference.tex
Writing up allnull experiments
Wrote subsection No Contamination Experiment, Contamination Experiment
Experiment_AllNull export numbers and figures

>>>>

\subsection{Uncontaminated Experiment}
The empirical null filter was demonstrated on an image where each pixel has i.i.d.~$\normal(0,1)$ test statistics. The test statistics after filtering should preserve its original distribution, or at least close to it. An experiment was conducted to investigate the empirical properties when filtering such as an image.

An example of a  $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt} is shown in Figure \ref{fig:inference_noContamination_images}. A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal. Because the empirical null mean and empirical null standard deviation are non-Normal random variables, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/inference/noContamination/allNullGaussianqq.eps}
	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
	\label{fig:inference_noContamination_qq}
\end{figure}

\begin{figure}[p]
	\centering
	\centerline{
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianunfiltered.eps}
		\caption{Unfiltered}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianfiltered.eps}
		\caption{Filtered}
	\end{subfigure}
	}
	\centerline{
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullmean.eps}
		\caption{Empirical null mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullstd.eps}
		\caption{Empirical null std}
	\end{subfigure}
	}
	\caption{A $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}. Also shown are the empirical null mean and empirical null std.}
	\label{fig:inference_noContamination_images}
\end{figure}

In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$ was simulated. The sample mean and sample variance of the post filtered test statistics were recorded. This was repeated \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} times by simulating another Gaussian image. Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradius1.txt}$ to $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradiusend.txt}$ were investigated.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianmean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianvariance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullgaussian}
\end{figure}

The results are shown in Figure \ref{fig:inference_allnullgaussian}.

\afterpage{\clearpage}
\subsection{Contaminated Experiment}
Consider a $\addNumber{../figures/inference/contamination/imageSize.txt}\times \addNumber{../figures/inference/contamination/imageSize.txt}$ Gaussian image with some contamination. For example let the pixels be $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where the null mean is a linear function
\begin{equation}
\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)
\end{equation}
where $(x_0,y_0)$ is the centre of the image and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. There are no defects or non-null pixels defined here, therefore any positive detections are false.

Figure \ref{fig:inference_contamination_images} shows an example of a contaminated image before and after filtering. When doing a hypothesis test, the contamination caused systematic error such that there are false positives on the two corners of the unfiltered image. The empirical null filter can recover the original image by extracting the systematic errors such as the plane, as shown by the empirical null mean, and the increase of variance, as shown by the empirical null std.

The QQ plot of the filtered test statistics, as shown in Figure \ref{fig:inference_contamination_qq}, shows that there may be a variance mismatch. A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would make more test statistics more likely to be tested as positive.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/inference/contamination/allNullPlaneqq.eps}
	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ contaminated Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
	\label{fig:inference_contamination_qq}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlaneunfiltered.eps}
				\caption{Unfiltered}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanefiltered.eps}
				\caption{Filtered}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullmean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullstd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{A $\addNumber{../figures/inference/contamination/imageSize.txt} \times \addNumber{../figures/inference/contamination/imageSize.txt}$ contaminated Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/contamination/radius.txt}. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. Also shown are the empirical null mean and empirical null std.}
	\label{fig:inference_contamination_images}
\end{figure}

An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image. Ideally the sample mean and sample variance should be 0 and 1 respectively. Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradius1.txt}$ to $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} times.

The results are shown in Figure \ref{fig:inference_allnullplane}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanemean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanevariance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullplane}
\end{figure}

\subsection{Contaminated Defect Experiment}
